---
title: "analysis"
author: "Yiming"
date: "11/9/2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(MASS)
library(graphics)
```

## read the file
```{r import-data}
data<-read.table(file = 'data/all_subjects_transitional_probability.txt', header = TRUE)
```

## linear regression of total counts
```{r linear-regression-total}
fit <- lm(total ~ Condition+Group, data=data)  # build linear regression model on full data
summary(fit)
library(nlme)
library(contrast)
contrast(fit,
         a = list(Group = "U",Condition=levels(df$Condition)),
         b = list(Group = "T",Condition=levels(df$Condition)))
```
```{r linear-regression-total-interaction}
fit.inte <- lm(total ~ Condition*Group, data=data)  # build linear regression model with interaction
summary(fit.inte)
```
```{r boxplot-total}
boxplot(total~Group*Condition, data=data, 
  col=(c("gold","darkgreen")),
  main="total translational counts", xlab="Condition and group")
```


```{r plot-total}
library(dplyr)
df2<-data %>%
  group_by(Condition, Group) %>%
  summarize(total.mean=mean(total),
            n=n(),
            total.se=sd(total)/sqrt(n))

ggplot(df2, aes(x=Condition, y=total.mean, group=Group, color=Group))+
         geom_line()+
        labs(x="condition", y="Total counts") +
         ggtitle('total translational counts') +
       scale_colour_hue(name="group",    #Legend label, use darker colors
                      breaks=c("T", "U"),
                    labels=c("Typically developing adults", "Down symdrone adults"))+
        geom_pointrange(aes(ymin=total.mean-total.se, ymax=total.mean+total.se))
  
```
# Other useful functions 
coefficients(fit) # model coefficients
confint(fit, level=0.95) # CIs for model parameters 
fitted(fit) # predicted values
residuals(fit) # residuals
anova(fit) # anova table 
vcov(fit) # covariance matrix for model parameters 
influence(fit) # regression diagnostics
# K-fold cross-validation
library(DAAG)
cv.lm(df=mydata, fit, m=3) # 3 fold cross-validation

```{r plot-total}
layout(matrix(c(1,2,3,4),2,2)) # optional 4 graphs/page 
plot(fit)
```


```{r manova-test}
# MANOVA test
res.man <- manova(cbind(AA,AB,AC,AX,BA,BB,BC,BX,CA,CB,CC,CX,XA,XB,XC,XX) ~ Condition+Group, data = data)
summary(res.man)
summary.aov(res.man)
```

Also, I noticed that in LP condition, there is relatively high percentage of “unclassified” and “saccade” (34.48%).   33.46% in emo, 35.12% in clock, 33.94% in soc.

## linear regression of total counts from A
```{r linear-regression-total}
data$A<-rowSums(data[,4:7] )
fit.a <- lm(A ~ Condition+Group, data=data)  # build linear regression model on full data
summary(fit.a)
```
## linear regression of total counts from A
```{r linear-regression-total}
data$A1<-rowSums(data[,5:7] ) # from A to distractors (B,C,X)
fit.a1 <- lm(A1 ~ Condition+Group, data=data)  # build linear regression model on full data
summary(fit.a1)
```

```{r linear-regression-AB-AC-AX}
data_percent=apply(data[1:120,4:7], 1, function(x){x*100/sum(x,na.rm=T)})
data$A2<-data_percent[1,] # the percentage of AA in sum of AA,AB,AC and AX, so 1-A2 is the likelihood to convert fixation from A to distractor B,C,X
fit.a2 <- lm(A2 ~ Condition+Group, data=data)  # build linear regression model on full data
summary(fit.a2)
```

```{r linear-regression-AC}
fit.a2 <- lm(AC ~ Condition+Group, data=data)  # build linear regression model on full data
summary(fit.a2)
```

```{r chi-Square}
data %>%
  group_by(Group, Condition) %>%
  summarise(AA=mean(AA),
            AB=mean(AB),
            AC=mean(AC),
            AX=mean(AX)) ->df2

#create color palette:
library(RColorBrewer)
coul = brewer.pal(4, "Pastel2") 
 
#Transform this data in %
data_percentage=apply(df2[1:8,3:6], 1, function(x){x*100/sum(x,na.rm=T)})
colnames(data_percentage) <- c("clock_T","emo_T","LP_T","soc_T","clock_U","emo_U","LP_U","soc_U")
rownames(data_percentage) <- c("AA","AB","AC","AX")

# Make a stacked barplot--> it will be in %!
bar<-barplot(data_percentage, col=coul , border="white", main="Percentage of AOI from target to the other categories") +
     legend(x="bottom", cex=0.7, c("Target AOI","Related AOI","distractors","white background"))
```

```{r chi-square}
# null hypothesis: given the total eye movement from target has no significant difference, the two groups of participants have the same likelihood to have eye movement to 4 categories in each condition. OR, we can say there is no association between groups and conditions.
# expected dataframe is group by row, condition by col.  
df3<-df2[, 3:6]  # if I muliply it with 100, it is significant. But shall I?
# row.names(df3) <- paste(df2$Condition, df2$Group, sep = "_")
# df4<-matrix(df3)
# # set as table
# 
# df4 <- as.table(df4)
# dimnames(df4) <- list(Condition = c("clock_T","emo_T", "LP_T", "soc_T", "clock_U","emo_U", "LP_U", "soc_U"),
#                       TC = c("AA","AB","AC","AX","nonAA","AAAB"))
#                                   
# df4<-as.table(df3)
chisq<-chisq.test(df3, simulate.p.value = TRUE) # df disappear?
chisq<-chisq.test(df3) 
# Observed counts
chisq$observed
round(chisq$expected,2)
# Pearson residuals can be easily extracted from the output of the function chisq.test():
round(chisq$residuals, 3)
# Contibution in percentage (%)
contrib <- 100*chisq$residuals^2/chisq$statistic
round(contrib, 3)
# printing the p-value
chisq$p.value
# printing the mean
chisq$estimate
# For such small counts, you could use Fisher's exact test:
fisher.test(df3)
```

```{r chi-square-AA-AB-AC-AX}
# null hypothesis: given the total eye movement from target has no significant difference, the two groups of participants have the same likelihood to have eye movement to 4 categories in each condition. OR, we can say there is no association between groups and conditions.
# expected dataframe is group by row, condition by col.  
chisq.clock<-chisq.test(df3[c(1,5),], correct=FALSE) 
chisq.clock
chisq.emo<-chisq.test(df3[c(2,6),], correct=FALSE) 
chisq.emo
chisq.LP<-chisq.test(df3[c(3,7),], correct=FALSE) 
chisq.LP
chisq.soc<-chisq.test(df3[c(4,8),], correct=FALSE) 
chisq.soc
chisq.T<-chisq.test(df3[1:4,], correct=FALSE) 
chisq.T
chisq.U<-chisq.test(df3[5:8,], correct=FALSE) 
chisq.U
```

```{r chi-square-AAABAC}
# null hypothesis: given the total eye movement from target has no significant difference, the two groups of participants have the same likelihood to have eye movement to 4 categories in each condition. OR, we can say there is no association between groups and conditions.
# expected dataframe is group by row, condition by col. 
chisq.clock<-chisq.test(df3[c(1,5),1:3], correct=FALSE) 
chisq.clock
chisq.emo<-chisq.test(df3[c(2,6),1:3], correct=FALSE) 
chisq.emo
chisq.LP<-chisq.test(df3[c(3,7),1:3], correct=FALSE) 
chisq.LP
chisq.soc<-chisq.test(df3[c(4,8),1:3], correct=FALSE) 
chisq.soc
chisq.T<-chisq.test(df3[1:4,1:3], correct=FALSE) 
chisq.T
chisq.U<-chisq.test(df3[5:8,1:3], correct=FALSE) 
chisq.U
```

```{r chi-square-AA-nonAA}
df3$nonAA<-rowSums( df3[,2:4] )  
chisq.clock<-chisq.test(df3[c(1,5),c(1,5)], correct=FALSE) 
chisq.clock
chisq.emo<-chisq.test(df3[c(2,6),c(1,5)], correct=FALSE) 
chisq.emo
chisq.LP<-chisq.test(df3[c(3,7),c(1,5)], correct=FALSE) 
chisq.LP
chisq.soc<-chisq.test(df3[c(4,8),c(1,5)], correct=FALSE) 
chisq.soc
chisq.T<-chisq.test(df3[1:4,c(1,5)], correct=FALSE) 
chisq.T
chisq.U<-chisq.test(df3[5:8,c(1,5)], correct=FALSE) 
chisq.U
```

```{r chi-square-AAAB-AC}
df3$AAAB<-rowSums( df3[,1:2] )  
chisq.clock<-chisq.test(df3[c(1,5),c(3,6)], correct=FALSE) 
chisq.clock
chisq.emo<-chisq.test(df3[c(2,6),c(3,6)], correct=FALSE) 
chisq.emo
chisq.LP<-chisq.test(df3[c(3,7),c(3,6)], correct=FALSE) 
chisq.LP
chisq.soc<-chisq.test(df3[c(4,8),c(3,6)], correct=FALSE) 
chisq.soc
chisq.T<-chisq.test(df3[1:4,c(3,6)], correct=FALSE) 
chisq.T
chisq.U<-chisq.test(df3[5:8,c(3,6)], correct=FALSE) 
chisq.U
```

```{r chi-square-sum-of-A}
df3$A<-rowSums( df3[,1:4] )  # if I muliply it with 100, it is significant. But shall I?
# row.names(df3) <- paste(df2$Condition, df2$Group, sep = "_")
df_A<-df3[,7]
df_A<--data.matrix(df_A)
df_A <- matrix(df_A, nrow=2)
# set as table
df_A <- as.table(df-A)
dimnames(df_A) <- list(group=c("T","U") , 
                      Condition = c("clock","emo", "LP", "soc"))
df_A<- df_A[,-4]
chisq.test(df_A)
```

```{r chi-square-AC}
df_AC<-df3[,3]
df_AC<-data.matrix(df_AC)
df_AC <- matrix(df_AC, nrow=2)
# set as table
df_AC <- as.table(df_AC)
dimnames(df4) <- list(group=c("T","U") , 
                      Condition = c("clock","emo", "LP", "soc"))
df_AC<- df_AC[,-4]
chisq.test(df_AC)
```