---
title: "analysis"
author: "Yiming"
date: "11/9/2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## read the file
```{r import-data}
df<-read.table(file = 'data/all_subjects_transitional_probability.txt', header = TRUE)
```

## linear regression of total counts
```{r linear-regression-total}
fit <- lm(total ~ Condition+Group, data=df)  # build linear regression model on full data
summary(fit)
library(nlme)
library(contrast)
contrast(fit,
         a = list(group = "U"),
         b = list(group = "T"))
```
```{r linear-regression-total-interaction}
fit.inte <- lm(total ~ Condition*Group, data=df)  # build linear regression model on full data
summary(fit.inte)
```
```{r boxplot-total}
boxplot(total~Group*Condition, data=df, 
  col=(c("gold","darkgreen")),
  main="total translational counts", xlab="Condition and group")
```
```{r plot-total}
library(dplyr)
df2<-df %>%
  group_by(Condition, Group) %>%
  summarize(total.mean=mean(total),
            total.se=sd(total)/length(total))

ggplot(df2, aes(x=Condition, y=total.mean, group=Group, color=Group))+
         geom_line()+
        labs(x="condition", y="Total counts") +
         ggtitle('total translational counts') +
       scale_colour_hue(name="group",    #Legend label, use darker colors
                      breaks=c("T", "U"),
                    labels=c("Typically developing adults", "Down symdrone adults"))+
        geom_pointrange(aes(ymin=total.mean-total.se, ymax=total.mean+total.se))
  
```
# Other useful functions 
coefficients(fit) # model coefficients
confint(fit, level=0.95) # CIs for model parameters 
fitted(fit) # predicted values
residuals(fit) # residuals
anova(fit) # anova table 
vcov(fit) # covariance matrix for model parameters 
influence(fit) # regression diagnostics
# K-fold cross-validation
library(DAAG)
cv.lm(df=mydata, fit, m=3) # 3 fold cross-validation

```{r plot-total}
layout(matrix(c(1,2,3,4),2,2)) # optional 4 graphs/page 
plot(fit)
```


```{r manova-test}
# MANOVA test
res.man <- manova(cbind(AA,AB,AC,AX,BA,BB,BC,BX,CA,CB,CC,CX,XA,XB,XC,XX) ~ Condition+Group, data = df)
summary(res.man)
summary.aov(res.man)
```