---
title: "analysis"
author: "Yiming"
date: "11/9/2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(MASS)
library(graphics)
```

## read the file
```{r import-data}
data<-read.table(file = 'data/all_subjects_transitional_probability.txt', header = TRUE)
```

## linear regression of total counts
```{r linear-regression-total}
fit <- lm(total ~ Condition+Group, data=data)  # build linear regression model on full data
summary(fit)
library(nlme)
library(contrast)
contrast(fit,
         a = list(Group = "U",Condition=levels(df$Condition)),
         b = list(Group = "T",Condition=levels(df$Condition)))
```
```{r linear-regression-total-interaction}
fit.inte <- lm(total ~ Condition*Group, data=data)  # build linear regression model with interaction
summary(fit.inte)
```
```{r boxplot-total}
boxplot(total~Group*Condition, data=data, 
  col=(c("gold","darkgreen")),
  main="total translational counts", xlab="Condition and group")
```


```{r plot-total}
library(dplyr)
df2<-data %>%
  group_by(Condition, Group) %>%
  summarize(total.mean=mean(total),
            n=n(),
            total.se=sd(total)/sqrt(n))

ggplot(df2, aes(x=Condition, y=total.mean, group=Group, color=Group))+
         geom_line()+
        labs(x="condition", y="Total counts") +
         ggtitle('total translational counts') +
       scale_colour_hue(name="group",    #Legend label, use darker colors
                      breaks=c("T", "U"),
                    labels=c("Typically developing adults", "Down symdrone adults"))+
        geom_pointrange(aes(ymin=total.mean-total.se, ymax=total.mean+total.se))
  
```
# Other useful functions 
coefficients(fit) # model coefficients
confint(fit, level=0.95) # CIs for model parameters 
fitted(fit) # predicted values
residuals(fit) # residuals
anova(fit) # anova table 
vcov(fit) # covariance matrix for model parameters 
influence(fit) # regression diagnostics
# K-fold cross-validation
library(DAAG)
cv.lm(df=mydata, fit, m=3) # 3 fold cross-validation

```{r plot-total}
layout(matrix(c(1,2,3,4),2,2)) # optional 4 graphs/page 
plot(fit)
```


```{r manova-test}
# MANOVA test
res.man <- manova(cbind(AA,AB,AC,AX,BA,BB,BC,BX,CA,CB,CC,CX,XA,XB,XC,XX) ~ Condition+Group, data = data)
summary(res.man)
summary.aov(res.man)
```

Also, I noticed that in LP condition, there is relatively high percentage of “unclassified” and “saccade” (34.48%).   33.46% in emo, 35.12% in clock, 33.94% in soc.

## linear regression of total counts from A
```{r linear-regression-total}
data$A<-rowSums(data[,4:7] )
fit.a <- lm(A ~ Condition+Group, data=data)  # build linear regression model on full data
summary(fit.a)
```

```{r chi-Square}
data %>%
  group_by(Group, Condition) %>%
  summarise(AA=mean(AA),
            AB=mean(AB),
            AC=mean(AC),
            AX=mean(AX)) ->df2

#create color palette:
library(RColorBrewer)
coul = brewer.pal(4, "Pastel2") 
 
#Transform this data in %
data_percentage=apply(df2[1:8,3:6], 1, function(x){x*100/sum(x,na.rm=T)})
colnames(data_percentage) <- c("clock_T","emo_T","LP_T","soc_T","clock_U","emo_U","LP_U","soc_U")
rownames(data_percentage) <- c("AA","AB","AC","AX")

# Make a stacked barplot--> it will be in %!
bar<-barplot(data_percentage, col=coul , border="white", main="Percentage of AOI from target to the other categories") +
     legend(x="bottom", cex=0.7, c("Target AOI","Related AOI","distractors","white background"))
```

```{r chi-square}
# null hypothesis: given the total eye movement from target has no significant difference, the two groups of participants have the same likelihood to have eye movement to 4 categories in each condition. OR, we can say there is no association between groups and conditions.
# expected dataframe is group by row, condition by col.  
df3<-df2[, 3:6]
row.names(df3) <- paste(df2$Condition, df2$Group, sep = "_")
chisq<-chisq.test(df3, correct=FALSE) 
# Observed counts
chisq$observed
round(chisq$expected,2)
# Pearson residuals can be easily extracted from the output of the function chisq.test():
round(chisq$residuals, 3)
# Contibution in percentage (%)
contrib <- 100*chisq$residuals^2/chisq$statistic
round(contrib, 3)
# printing the p-value
chisq$p.value
# printing the mean
chisq$estimate
```

```{r chi-square}
# null hypothesis: given the total eye movement from target has no significant difference, the two groups of participants have the same likelihood to have eye movement to 4 categories in each condition. OR, we can say there is no association between groups and conditions.
# expected dataframe is group by row, condition by col.  
chisq.clock<-chisq.test(df3[c(1,5),], correct=FALSE) 
chisq.clock
chisq.emo<-chisq.test(df3[c(2,6),], correct=FALSE) 
chisq.emo
chisq.LP<-chisq.test(df3[c(3,7),], correct=FALSE) 
chisq.LP
chisq.soc<-chisq.test(df3[c(4,8),], correct=FALSE) 
chisq.soc
chisq.T<-chisq.test(df3[1:4,], correct=FALSE) 
chisq.T
chisq.U<-chisq.test(df3[5:8,], correct=FALSE) 
chisq.U
```