---
title: "Calculate display statistics"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: html_document
params:
  project_dir: '~/Box/R01 Project 2 Data for Yiming&Rick/R01A-C files for transitional probabilities'
---

# Purpose

To calculate basic statistics about the displays shown to participants.

# Set-up

```{r}
library(tidyverse)
```

# Import single file

List the files in `csv/`.

```{r}
csv_files <- list.files('csv', pattern = '\\.csv$', full.names = TRUE, )
csv_files
```

Import the last one, e.g., `csv_files[5]`.

```{r}
df <- readr::read_csv(csv_files[5])
```

# Summarize single file

Participant file includes two runs with 'White' and 'Color'.

The `StudioTestName` variable has values \{`W01`, `CR01`\}.

```{r}
df_white_all <- df %>%
  dplyr::filter(., str_detect(StudioTestName, 'WO1'))
df_color_all <- df %>%
  dplyr::filter(., str_detect(StudioTestName, 'CRO1'))
```

## Unique media names

Each experimental trial consists of a fixation `Slide03.jpg`, followed by a prompt `*.wmv`, and then a display `*.png`.

We can extract the main times for these events as follows.

```{r}
df_white <- df_white_all %>%
  dplyr::select(., ParticipantName, RecordingTimestamp, MediaName) %>%
  #dplyr::filter(., str_detect(MediaName, 'White')) %>%
  dplyr::arrange(., ParticipantName, RecordingTimestamp)

df_color <- df_color_all %>%
  dplyr::select(., ParticipantName, RecordingTimestamp, MediaName) %>%
  #dplyr::filter(., str_detect(MediaName, 'Color')) %>%
  dplyr::arrange(., ParticipantName, RecordingTimestamp)
```

```{r}
df_white_media <- df_white %>%
  dplyr::filter(., !is.na(MediaName),
                !str_detect(MediaName, 'Slide03.jpg'),
                !str_detect(MediaName, 'job')) %>%
  dplyr::arrange(., RecordingTimestamp) %>%
  dplyr::group_by(., MediaName) %>%
  dplyr::summarise(., event_start = min(RecordingTimestamp),
                   event_end = max(RecordingTimestamp)) %>%
  dplyr::arrange(., event_start)

df_color_media <- df_color %>%
  dplyr::filter(., !is.na(MediaName),
                !str_detect(MediaName, 'Slide03.jpg'),
                !str_detect(MediaName, 'job')) %>%
  dplyr::arrange(., RecordingTimestamp) %>%
  dplyr::group_by(., MediaName) %>%
  dplyr::summarise(., event_start = min(RecordingTimestamp),
                   event_end = max(RecordingTimestamp)) %>%
  dplyr::arrange(., event_start)
```

Now, let's try to estimate the trial number for the `.wmv` and `.png` files separately.

Write a helper function to detect unique values in this sequence.

The function moves along a sequence and only adds a new value when there is a change from the previous one.
It's not elegant or efficient, but it works.
I tried `unique()`, but had some issues.

```{r, eval=FALSE}
extract_media_value_sequence <- function(x) {
  not_nas <- !(is.na(x))
  these_xs <- NULL
  prior_x <- ""
  x_clean <- x[not_nas]
  for (i in 1:length(x_clean)) {
    this_x <- x_clean[i]
    if (!is.na(this_x)) {
      if (this_x != prior_x) {
        these_xs <- c(these_xs, this_x)
      }
      prior_x <- this_x      
    }
  }
  these_xs
}
```


### White events

The strategy here is convoluted, but I think it works.

1. Pick the 'prompt' (.wmv) and 'layout' (.png) events separately, and add a `trial_n` variable.
2. Merge the two types and compute `trial_start` and `trial_end`.

```{r}
df_white_media_png <- df_white_media %>%
  dplyr::arrange(., event_start) %>%
  dplyr::filter(., str_detect(MediaName, 'png')) %>%
  dplyr::mutate(., trial_n = 1:length(MediaName))

df_white_media_wmv <- df_white_media %>%
  dplyr::arrange(., event_start) %>%
  dplyr::filter(., str_detect(MediaName, 'wmv')) %>%
  dplyr::mutate(., trial_n = 1:length(MediaName))

df_white_merge <- rbind(df_white_media_png, df_white_media_wmv)
df_white_merge <- df_white_merge %>%
  dplyr::arrange(., trial_n, event_start) %>%
  dplyr::group_by(., trial_n) %>%
  dplyr::summarize(., trial_n, MediaName, event_start, event_end, 
                   trial_start = min(event_start), trial_end = max(event_end))
```

3. Create separate data frames again for the 'display' and 'prompt' portions and extract for each type the relevant metadata from the `MediaName` variable.

4. Then, use `dplyr::inner_join()` to combine the data frames and drop unneeded variables.

```{r}
df_white_disp_parse <- df_white_merge %>%
  dplyr::filter(., str_detect(MediaName, 'png')) %>%
  dplyr::mutate(., 
                       bgnd = str_match(MediaName, "(Color|White)_(SOC|wide|corners|[Cc]lock)")[,2],
                       layout = str_match(MediaName, "(Color|White)_(SOC|wide|corners|[Cc]lock)")[,3]) %>%
  dplyr::select(., trial_n, bgnd, layout)

df_white_prompt_parse <- df_white_merge %>%
  dplyr::filter(., str_detect(MediaName, 'wmv')) %>%
  dplyr::mutate(., speaker = str_match(MediaName, "([A-Za-z]+)_([a-z]+)\\.wmv")[,2],
                target = str_match(MediaName, "([A-Za-z]+)_([a-z]+)\\.wmv")[,3])

df_white_trials <- dplyr::inner_join(df_white_disp_parse, df_white_prompt_parse, by="trial_n") %>%
  dplyr::select(., trial_n, layout, trial_start, trial_end, speaker, target, bgnd, layout)
```

Let's compute and plot `trial_ms` just to see if this works.

```{r}
df_white_trials %>%
  dplyr::mutate(., trial_ms = trial_end - trial_start) %>%
  ggplot() +
  aes(trial_ms) +
  geom_histogram(bins = 10)
```

And how about `trial_ms` by some of the conditions.

```{r}
 df_white_trials %>%
  dplyr::mutate(., trial_ms = trial_end - trial_start) %>%
  ggplot() +
  aes(layout, trial_ms) +
  geom_violin(bins = 10) +
  geom_point()
```

### Color events

We'll repeat the same procedure for the 'Color' condition.

```{r}
df_color_media_png <- df_color_media %>%
  dplyr::arrange(., event_start) %>%
  dplyr::filter(., str_detect(MediaName, 'png')) %>%
  dplyr::mutate(., trial_n = 1:length(MediaName))

df_color_media_wmv <- df_color_media %>%
  dplyr::arrange(., event_start) %>%
  dplyr::filter(., str_detect(MediaName, 'wmv')) %>%
  dplyr::mutate(., trial_n = 1:length(MediaName))

df_color_merge <- rbind(df_color_media_png, df_color_media_wmv)

df_color_merge <- df_color_merge %>%
  dplyr::arrange(., trial_n, event_start) %>%
  dplyr::group_by(., trial_n) %>%
  dplyr::summarize(., trial_n, MediaName, event_start, event_end, 
                   trial_start = min(event_start), trial_end = max(event_end)) %>%
  dplyr::mutate(., trial_ms = trial_end - trial_start)

df_color_disp_parse <- df_color_merge %>%
  dplyr::filter(., str_detect(MediaName, 'png')) %>%
  dplyr::mutate(., 
                       bgnd = str_match(MediaName, "(Color|White)_(SOC|wide|corners|[Cc]lock)")[,2],
                       layout = str_match(MediaName, "(Color|White)_(SOC|wide|corners|[Cc]lock)")[,3]) %>%
  dplyr::select(., trial_n, bgnd, layout)

df_color_prompt_parse <- df_color_merge %>%
  dplyr::filter(., str_detect(MediaName, 'wmv')) %>%
  dplyr::mutate(., speaker = str_match(MediaName, "([A-Za-z]+)_([a-z]+)\\.wmv")[,2],
                target = str_match(MediaName, "([A-Za-z]+)_([a-z]+)\\.wmv")[,3])

df_color_trials <- dplyr::inner_join(df_color_disp_parse, df_color_prompt_parse, by="trial_n") %>%
  dplyr::select(., trial_n, layout, trial_start, trial_end, speaker, target, bgnd, layout)
```


```{r}
df_color_trials %>%
  dplyr::mutate(., trial_ms = trial_end - trial_start) %>%
  ggplot() +
  aes(trial_ms) +
  geom_histogram(bins = 10)
```

```{r}
 df_color_trials %>%
  dplyr::mutate(., trial_ms = trial_end - trial_start) %>%
  ggplot() +
  aes(layout, trial_ms) +
  geom_violin(bins = 10) +
  geom_point()
```

This seems to be working.
Now, I can move on to parsing the fixations.

Now, put the previous into a function.

```{r}
make_trial_cond_df <- function(df) {
  df_media_png <- df %>%
    dplyr::arrange(., event_start) %>%
    dplyr::filter(., str_detect(MediaName, 'png')) %>%
    dplyr::mutate(., trial_n = 1:length(MediaName))
  
  df_media_wmv <- df %>%
    dplyr::arrange(., event_start) %>%
    dplyr::filter(., str_detect(MediaName, 'wmv')) %>%
    dplyr::mutate(., trial_n = 1:length(MediaName))
  
  df_merge <- rbind(df_media_png, df_media_wmv)
  
  df_merge <- df_merge %>%
    dplyr::arrange(., trial_n, event_start) %>%
    dplyr::group_by(., trial_n) %>%
    dplyr::summarize(
      .,
      trial_n,
      MediaName,
      event_start,
      event_end,
      trial_start = min(event_start),
      trial_end = max(event_end)
    )
  
  df_disp_parse <- df_merge %>%
    dplyr::filter(., str_detect(MediaName, 'png')) %>%
    dplyr::mutate(
      .,
      bgnd = str_match(MediaName, "(Color|White)_(SOC|wide|corners|[Cc]lock)")[, 2],
      layout = str_match(MediaName, "(Color|White)_(SOC|wide|corners|[Cc]lock)")[, 3]
    ) %>%
    dplyr::select(., trial_n, bgnd, layout)
  
  df_prompt_parse <- df_white_merge %>%
    dplyr::filter(., str_detect(MediaName, 'wmv')) %>%
    dplyr::mutate(
      .,
      speaker = str_match(MediaName, "([A-Za-z]+)_([a-z]+)\\.wmv")[, 2],
      target = str_match(MediaName, "([A-Za-z]+)_([a-z]+)\\.wmv")[, 3]
    )
  
  df_trials <- dplyr::inner_join(df_white_disp_parse,
                                 df_white_prompt_parse, by = "trial_n") %>%
    dplyr::select(.,
                  trial_n,
                  layout,
                  trial_start,
                  trial_end,
                  speaker,
                  target,
                  bgnd,
                  layout)
  df_trials
  
}
```

Test the function.

```{r}
make_trial_cond_df(df_white_media)
```

Ok, that hard work now seems finished.

## Duration

### White

```{r}
(tot_dur_ms <- max(df_white$RecordingTimestamp))
(secs <- tot_dur_ms/1000)
(min <- secs/60)
```

### Color

```{r}
(tot_dur_ms <- max(df_color$RecordingTimestamp))
(secs <- tot_dur_ms/1000)
(min <- secs/60)
```

-----

Old material.

## Displays


```{r white-conds}
white_conds <- extract_media_value_sequence(df_white$MediaName)
white_conds_df <- tibble(trial = 1:length(white_conds),
                             MediaName = white_conds)

layout_pattern <- "(Color|White)_(SOC|wide|corners|[Cc]lock)"
bgnd_layout <- str_match(white_conds_df$MediaName, layout_pattern)

white_conds_df <- white_conds_df %>%
  mutate(., bgnd = bgnd_layout[,2],
         layout = bgnd_layout[,3])

white_conds_df
```

Based on a visual inspection, it looks like the order of the layouts was randomized across the 'Color' and 'White' background conditions.

Let's turn this into a function.

```{r}
summarize_bgnd_layout <- function(df) {
  these_conds <- extract_media_value_sequence(df$MediaName)
  these_conds_df <- tibble(trial = 1:length(these_conds),
                           MediaName = these_conds)
  
  layout_pattern <- "(Color|White)_(SOC|wide|corners|[Cc]lock)"
  bgnd_layout <- str_match(these_conds_df$MediaName, layout_pattern)
  
  these_conds_df <- these_conds_df %>%
    mutate(., bgnd = bgnd_layout[,2],
           layout = bgnd_layout[,3])
  
  these_conds_df
}
```

Test the function.

```{r}
(summarize_bgnd_layout(df_white))
```

### Calculate start and stop time of displays

Let's see if we can calculate the start and stop time of the display conditions using `group_by()` and `summarize()`.

```{r}
df_white_disp_on_off <- df_white %>%
  dplyr::filter(., str_detect(MediaName, 'Color|White')) %>%
  dplyr::group_by(., MediaName) %>%
  dplyr::summarize(., trial_start = min(RecordingTimestamp),
                   trial_end = max(RecordingTimestamp)) %>%
  dplyr::arrange(., trial_start)

df_white_disp_on_off
```

Now, use this to create a new, improved trial summary function.

```{r}
summarize_trial_on_off <- function(df) {
  this_df <- dplyr::filter(df, str_detect(MediaName, 'Color|White')) %>%
    dplyr::group_by(., MediaName) %>%
    dplyr::summarize(., trial_start = min(RecordingTimestamp),
                   trial_end = max(RecordingTimestamp)) %>%
    dplyr::arrange(., trial_start)
  
  layout_pattern <- "(Color|White)_(SOC|wide|corners|[Cc]lock)"
  bgnd_layout <- str_match(this_df$MediaName, layout_pattern)
  
  this_df <- this_df %>%
    mutate(., bgnd = bgnd_layout[,2],
           layout = bgnd_layout[,3],
           trial = 1:dim(this_df)[1]) %>%
    dplyr::select(., trial, trial_start, trial_end, MediaName, bgnd, layout)

  this_df
}
```

Now test the function.

```{r}
df_white_on_off <- summarize_trial_on_off(df_white)
df_white_on_off
```

That works, so now let's report trial durations.

```{r}
df_white_on_off %>%
  dplyr::mutate(., trial_ms = trial_end - trial_start) %>%
  dplyr::select(., trial, trial_ms)
```

And let's plot them for white...

```{r}
df_white_on_off %>%
  dplyr::mutate(., trial_ms = trial_end - trial_start) %>%
  ggplot(.) +
  aes(x = layout, y = trial_ms) +
  geom_boxplot() +
  geom_point()
```

And for Color

```{r}
df_color_on_off <- summarize_trial_on_off(df_color)
df_color_on_off %>%
  dplyr::mutate(., trial_ms = trial_end - trial_start) %>%
  ggplot(.) +
  aes(x = layout, y = trial_ms) +
  geom_boxplot() +
  geom_point()
```

Recombine to make comparison plots easier.

```{r}
df_both <- rbind(df_white_on_off, df_color_on_off)

df_both %>%
  dplyr::mutate(., trial_ms = trial_end - trial_start) %>%
  ggplot(.) +
  aes(x = layout, y = trial_ms, group = bgnd) +
  facet_grid(bgnd ~ .) +
  geom_point()
```

So, it looks like the 'White' condition uses lowercase 'clock' while the 'Color' condition uses uppercase.

```{r}
df_both %>%
  dplyr::mutate(., trial_ms = trial_end - trial_start,
                layout = str_to_lower(layout)) %>%
  ggplot(.) +
  aes(x = layout, y = trial_ms) +
  facet_grid(bgnd ~ .) +
  geom_boxplot() +
  # put points on top of boxplot
  geom_point()
```

## Mouse events

Lets try to extract the mouse events.

```{r}
df_white_mouse <- df %>%
  dplyr::select(., ParticipantName, RecordingTimestamp, MediaName, MouseEventIndex,
                MouseEvent, `MouseEventX (ADCSpx)`, `MouseEventY (ADCSpx)`,
                `MouseEventX (MCSpx)`, `MouseEventY (MCSpx)`, FixationIndex) %>%
  dplyr::filter(., !is.na(MouseEvent),
                str_detect(MediaName, 'White')) %>%
  dplyr::arrange(., RecordingTimestamp) %>%
  dplyr::mutate(., elapsed_secs = RecordingTimestamp/1000)
str(df_white_mouse)
```

Now, let's turn into a function

```{r}
summarize_mouse_events <- function(df) {
  these_mouse_df <- df %>%
    dplyr::select(
      .,
      RecordingTimestamp,
      MediaName,
      MouseEventIndex,
      MouseEvent,
      `MouseEventX (ADCSpx)`,
      `MouseEventY (ADCSpx)`,
      `MouseEventX (MCSpx)`,
      `MouseEventY (MCSpx)`,
      FixationIndex
    ) %>%
    dplyr::filter(., !is.na(MouseEvent)) %>%
    dplyr::arrange(., RecordingTimestamp)
  
  layout_pattern <- "(Color|White)_(SOC|wide|corners|[Cc]lock)"
  bgnd_layout <- str_match(these_mouse_df$MediaName, layout_pattern)
  
  these_mouse_df <- these_mouse_df %>%
    mutate(., bgnd = bgnd_layout[, 2],
           layout = bgnd_layout[, 3])
  
  these_mouse_df <- these_mouse_df %>%
    dplyr::select(
      .,
      MouseEventIndex,
      RecordingTimestamp,
      MediaName,
      bgnd,
      layout,
      `MouseEventY (ADCSpx)`,
      `MouseEventX (MCSpx)`,
      `MouseEventY (MCSpx)`,
      FixationIndex
    )
  
  these_mouse_df
}
```

Now, test the function.

```{r}
dplyr::filter(df, str_detect(MediaName, 'White')) %>%
  summarize_mouse_events()
```

And for 'Color'.

```{r}
dplyr::filter(df, str_detect(MediaName, 'Color')) %>%
  summarize_mouse_events()
```

## Prompts

It's harder to pull out the "Color" and "White" conditions because the prompts have their own `MediaName` values that are duplicated across both conditions.
There is no date/timestamp to rely on.
We have to do this separately for the two conditions.

The `StudioTestName` variable has values \{`W01`, `CR01`\}.

```{r}
df_white <- df %>%
  dplyr::filter(., str_detect(StudioTestName, 'W01'))
df_color <- df %>%
  dplyr::filter(., str_detect(StudioTestName, 'CR01'))
```


```{r}
# Now prompts
# df_prompt_only <- df %>%
#   dplyr::filter(., )
#   dplyr::filter(., str_detect(MediaName, 'wmv')) %>%
#   dplyr::select(., RecordingTimestamp, MediaName) %>%
#   dplyr::group_by(., MediaName) %>%
#   dplyr::summarize(., prompt_start = min(RecordingTimestamp),
#                    prompt_end = max(RecordingTimestamp)) %>%
#   dplyr::arrange(., prompt_start)
# 
# 
# prompts_df <- tibble(MediaName = extract_media_value_sequence(df_TR_prompt_only$medianame))
# prompts_df$trial <- 1:dim(prompts_df)[1]
# 
# media_nm_pattern <- "([A-Z]{1}[a-z]+)_([a-z]+)"
# spkr_target <- str_match(prompts_df$medianame, media_nm_pattern)
# 
# prompts_df <- prompts_df %>%
#   mutate(., speaker = spkr_target[,2],
#          target = spkr_target[,3])
# 
# # drop medianame since prompt has its own medianame value 
# 
# prompts_df <- prompts_df %>%
#   dplyr::select(., -medianame)

```

## AOIs

The AOI columns need to be collapsed into a single variable.

```{r}
df_white_lower <- df %>%
  dplyr::filter(., str_detect(MediaName, 'Color')) %>%
  purrr::set_names(~ str_to_lower(.) %>%
                     str_replace_all("AOI|aoi", "") %>%
                     str_replace_all("\\[", ""))
  
df_white_longer <- df_white_lower %>%
  pivot_longer(
    cols = `1c-wide-swing]hit`:`32x-wide-all]hit_1`,
    names_pattern = "([0-9]+)([abcx])\\-([a-z]+)\\-([a-z\\-123]+)]hit_?(1?)",
    names_to = c("aoi_trial_index", "category", "layout", "aoi", "fix_here"),
    values_to = "count"
  )
```

