---
title: "Cumulative looking plots"
subtitle: "Version 5.0"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    toc: true
    toc_levels: 3
    toc_float: true
---

# Purpose

This document describes Rick Gilmore's efforts to create plots to visualize the accumulation of looking times to different categories of visual stimuli in one of the Wilkinson R01 projects.
The idea is to take as input a time series of fixations within a trial, categorized by the three categories--target-target (AA), target-semantically related (AB), target-distractor (AC), and target-white space (AX)--and show cumulative looking to across a trial.
Our thought is that this will help us visualize how the amount of fixation time is accumulating, including rates of accumulation and switches among different categories.
An extension would involve normalizing the horizontal axis (time), but the total response time and the vertical axis (accumulated time), but the total looking time.

This version of the analysis builds on a version 1.0 (`cumulative-looking-plot-v04.Rmd`).
I benefitted from a discussion with Yiming Qian about how to parse the columns beginning with `AOI`.

# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse) # for pipe %>% function
```

## Finding data

The relevant data are in Box.

The parent project folder is `~/Box/R01 Project 2 Data for Yiming&Rick/R01A-C files for transitional probabilities/`, and the files are in `.xlsx` format.

# Import data

First we list the fixation files.

```{r}
fix_files <- list.files('~/Box/R01 Project 2 Data for Yiming&Rick/R01A-C files for transitional probabilities', pattern = '\\.xlsx$', full.names = TRUE)

fix_files
```

I failed to use `read_xls()`, so I manually exported one of the files as a CSV.

```{r}
csv_files <- list.files('~/Box/R01 Project 2 Data for Yiming&Rick/R01A-C files for transitional probabilities', pattern = '\\.csv$', full.names = TRUE)
csv_files
```

Let's see if we can import the CSV.

```{r}
df <- readr::read_csv(csv_files[2])
```

# Data cleaning

I'm taking a new approach.

## Time series of media elements

```{r}
df_tr <- df %>%
  dplyr::filter(., ParticipantName == "TR")
```

```{r}
time_media <- df_tr %>%
  dplyr::select(., RecordingTimestamp, MediaName) %>%
  dplyr::mutate(., cue_on = if_else(str_detect(MediaName, '\\.wmv'),
                                    TRUE, FALSE)) %>%
  dplyr::mutate(., target_on = if_else(str_detect(MediaName, 'White|Color'),
                                       TRUE, FALSE)) %>%
  dplyr::mutate(., fix_pt_on = if_else(str_detect(MediaName, 'Slide03'),
                                       TRUE, FALSE)) %>%
  dplyr::mutate(., good_job_on = if_else(str_detect(MediaName, 'good|greatjob'), TRUE, FALSE)) %>%
  dplyr::mutate(., event_type = if_else(cue_on, 'cue_on',
                                        if_else(
                                          target_on,
                                          'target_on',
                                          if_else(
                                            fix_pt_on,
                                            'fix_pt_on',
                                            if_else(good_job_on, 
                                                    'good_job_on', MediaName))
                                        )))
```

Let's see if this can help us plot the time series of stimulus events.

```{r}
time_media %>%
  dplyr::filter(., RecordingTimestamp < 40000,
                !is.na(MediaName)) %>%
  ggplot(.) +
  aes(x = RecordingTimestamp, y = event_type, color=event_type) +
  geom_point()
```





Let's parse and reformat the column names.

```{r}
df_new <- a_ds_df %>%
  purrr::set_names(~ str_to_lower(.) %>%
                     str_replace_all("AOI|aoi", "") %>%
                     str_replace_all("\\[", ""))
```

Let's then select one participant.

```{r}
p_ids <- unique(df_new$participantname)
```

```{r}
df_new_1 <- df_new[df_new$participantname == "TR",]
```

Let's see if we can gather or `pivot_longer`.

```{r, eval=FALSE}
df_longer <- df_new_1 %>%
  pivot_longer(
    cols = `1c-wide-swing]hit`:`32x-wide-all]hit_1`,
    names_pattern = "([0-9]+)([abcx])\\-([a-z]+)\\-([a-z\\-123]+)]hit_?(1?)",
    names_to = c("trial", "category", "layout", "target", "fix_here"),
    values_to = "count"
  ) %>%
  filter(., count > 0)
```

```{r}
df_longer <- df_new_1 %>%
  pivot_longer(
    cols = `1c-wide-swing]hit`:`32x-wide-all]hit_1`,
    names_pattern = "([0-9]+)([abcx])\\-([a-z]+)\\-([a-z\\-123]+)]hit_?(1?)",
    names_to = c("trial", "category", "layout", "aoi", "fix_here"),
    values_to = "count"
  )
```

Extract `.wmv` values from `medianame` for each trial.

```{r}
trial_target <- df_longer %>%
  dplyr::select(., trial, medianame, count) %>%
  dplyr::filter(., str_detect(medianame, '\\.wmv'))

unique(trial_target)
```


Let's trim some of the other fields I don't need.

```{r}
df_longer <- df_longer %>%
  dplyr::select(., -studioprojectname, 
                -studiotestname,
                -`participant type]value`,
                -mouseeventindex,
                -mouseevent,
                -`mouseeventx (adcspx)`,
                -`mouseeventy (adcspx)`,
                -`mouseeventx (mcspx)`,
                -`mouseeventy (mcspx)`,
                -gazeeventtype,
                -`fixationpointx (mcspx)`,
                -`fixationpointy (mcspx)`) %>%
  dplyr::arrange(., trial, fixationindex, recordingtimestamp)
```

Rename some fie

```{r}
df_longer <- df_longer %>%
  dplyr::rename(., pid = participantname,
                ms = recordingtimestamp,
                fix_index = fixationindex,
                fix_ms = gazeeventduration,
  ) %>%
  dplyr::mutate(., trial = as.numeric(trial))

write_csv(df_longer, '~/Desktop/longer.csv')
```

Note that the `category` variable for the AOI includes `x` for trials where the participant is also looking at one of the other categories.

Krista thinks we can filter that for now since we don't really care about the whitespace fixations at this point.
We'll also see if the `fix_here` flag works and filter on it.

```{r}
df_longer <- df_longer %>%
  dplyr::filter(., category %in% c('a', 'b', 'c')) %>%
  dplyr::arrange(., trial, ms)
```

```{r}
n_aois_per <- df_longer %>%
  dplyr::arrange(., trial, fix_index, ms) %>%
  dplyr::group_by(., ms) %>%
  dplyr::summarize(., n_aois = cumsum(count))

these_aois <- (n_aois_per$n_aois == 1)

df_longer <- df_longer %>%
  dplyr::arrange(., trial, fix_index, ms) 

df_merge <- df_longer %>%
  dplyr::mutate(., n_aois_per_fix = n_aois_per$n_aois) %>%
  dplyr::filter(., n_aois_per_fix == 1)
```

That seems to work, hacky or no.

Let's plot a condition to see if our scheme works.

# Plot one participant and one trial

How many trials?

```{r}
unique(df_merge$trial)
```

Looks like there are 32.

Select fixations for trial 1.

```{r}
this_trial <- df_merge %>%
  filter(., trial == 1)
```

```{r}
this_trial %>%
  ggplot(.) +
  aes(x=fix_index, y=fix_ms) +
  geom_point()
```

Let's generate cumulative sums.

```{r}
this_trial_fixations <- this_trial %>%
  dplyr::group_by(., category, fix_index) %>%
  dplyr::summarize(., fix_ms = mean(fix_ms),
                   fix_start = min(ms)) %>%
  dplyr::arrange(., fix_index)

this_trial_fixations_cum_sum <- this_trial_fixations %>%
  dplyr::group_by(., category) %>%
  dplyr::summarize(., cum_fix = cumsum(fix_ms), fix_start = fix_start) %>%
  dplyr::arrange(., category, fix_start)
```

```{r}
this_trial_fixations_cum_sum %>%
  ggplot(.) +
  aes(x = fix_start, y = cum_fix, color = category) +
  geom_point() +
  geom_line()
```
 
 ## Same participant, multiple trials
 
```{r}
df_merge <- df_merge %>%
  dplyr::mutate(., trial = as.numeric(trial))

these_fixations <- df_merge %>%
  dplyr::group_by(., trial, layout, target, fix_index, category) %>%
  dplyr::summarize(., fix_ms = mean(fix_ms),
                   fix_start = min(ms)) %>%
  dplyr::arrange(., trial, fix_index, category)

these_fixations_cum_sum <- these_fixations %>%
  dplyr::arrange(., fix_start) %>%
  dplyr::group_by(., trial, category) %>%
  dplyr::summarize(., trial = trial, layout = layout,
                   target = target,
                   fix_start = fix_start, category = category, 
                   cum_fix = cumsum(fix_ms)) %>%
  dplyr::arrange(., trial, fix_start, category)
```
 
```{r}
plot_this_trial <- function(select_trial = 1, save_it = FALSE) {
  this_trial <- dplyr::filter(these_fixations_cum_sum, trial == select_trial)
  p <- ggplot(this_trial) +
    aes(x = fix_start, y = cum_fix, color = category) +
    geom_point() +
    ggtitle(paste0("Participant TR | Trial ", this_trial$trial, ' | ',
                   this_trial$target, ' | ', this_trial$layout)) +
    geom_line()
  
  if (save_it) {
  ggsave(paste0('img/', 'TR-', this_trial$trial, '-', 
                this_trial$target, '-', this_trial$layout, '.png'),
         device = 'png')    
  }
  p
}

plot_this_trial(4)
```

```{r}
purrr::map(1:32, plot_this_trial)
```
