---
title: "Cumulative Looking Plots"
subtitle: "Version 6.0"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    toc: true
    toc_levels: 3
    toc_float: true
---

# Purpose

This document describes Rick Gilmore's efforts to create plots to visualize the accumulation of looking times to different categories of visual stimuli in one of the Wilkinson R01 projects.
The idea is to take as input a time series of fixations within a trial, categorized by the three categories--target-target (AA), target-semantically related (AB), target-distractor (AC), and target-white space (AX)--and show cumulative looking to across a trial.
Our thought is that this will help us visualize how the amount of fixation time is accumulating, including rates of accumulation and switches among different categories.
An extension would involve normalizing the horizontal axis (time), but the total response time and the vertical axis (accumulated time), but the total looking time.

This version of the analysis builds on a version 1.0 (`cumulative-looking-plot-v04.Rmd`).
I benefitted from a discussion with Yiming Qian about how to parse the columns beginning with `AOI`.

# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse) # for pipe %>% function
```

## Finding data

The relevant data are in Box.

The parent project folder is `~/Box/R01 Project 2 Data for Yiming&Rick/R01A-C files for transitional probabilities/`, and the files are in `.xlsx` format.

# Import data

First we list the fixation files.

```{r}
fix_files <- list.files('~/Box/R01 Project 2 Data for Yiming&Rick/R01A-C files for transitional probabilities', pattern = '\\.xlsx$', full.names = TRUE)

fix_files
```

Convert to CSV and import one.

```{r}
csv_files <- list.files('~/Box/R01 Project 2 Data for Yiming&Rick/R01A-C files for transitional probabilities', pattern = '\\.csv$', full.names = TRUE)
csv_files
```

```{r}
df <- readr::read_csv(csv_files[2])
```

# Data cleaning

Let's parse and reformat the column names.

```{r}
df_new <- df %>%
  purrr::set_names(~ str_to_lower(.) %>%
                     str_replace_all("AOI|aoi", "") %>%
                     str_replace_all("\\[", ""))
```

Let's then select one participant.

```{r}
p_ids <- unique(df_new$participantname)
p_ids
```

Let's pick the first one.

```{r}
df_TR <- df_new[df_new$participantname == "TR",]
```

```{r}
df_TR_longer <- df_TR %>%
  pivot_longer(
    cols = `1c-wide-swing]hit`:`32x-wide-all]hit_1`,
    names_pattern = "([0-9]+)([abcx])\\-([a-z]+)\\-([a-z\\-123]+)]hit_?(1?)",
    names_to = c("trial", "category", "layout", "aoi", "fix_here"),
    values_to = "count"
  )
```

Filter based on `medianame`.
The 'target' samples have 'White' or 'Color' in `medianame`.
But we have to extract the target from the `medianame` used for the prompt.

```{r}
trial_prompts <- df_TR_longer %>%
  dplyr::select(., trial, medianame) %>%
  dplyr::filter(., !is.na(medianame),
                "\\.wmv" %in% medianame) %>%
  dplyr::group_by(trial) %>%
  dplyr::summarise(target_stim = str_extract(medianame,
                                             "_([a-z]+)\\.wmv"))
```
```{r}
trial_prompts <- df_TR_longer %>%
  dplyr::select(., trial, medianame) %>%
  dplyr::filter(., !is.na(medianame),
                str_detect(medianame, '\\.wmv')) 

media_nm_pattern <- "([A-Z]{1}[a-z]+)_([a-z]+)"
spkr_target <- str_match(trial_prompts$medianame, media_nm_pattern)

trial_prompts$spkr <- spkr_target[,2]
trial_prompts$target <- spkr_target[,3]
```


```{r}
df_TR_longer_disp_only <- df_TR_longer %>%
  dplyr::filter(., str_detect(medianame, 'White|Color'))

dim(df_TR_longer_disp_only)
```

Still seems long, but let's trim some columns.

```{r}

df_TR_longer_disp_only <- df_TR_longer_disp_only %>%
  dplyr::select(., -studioprojectname, 
                -studiotestname,
                -`participant type]value`,
                -mouseeventindex,
                -mouseevent,
                -`mouseeventx (adcspx)`,
                -`mouseeventy (adcspx)`,
                -`mouseeventx (mcspx)`,
                -`mouseeventy (mcspx)`,
                -gazeeventtype,
                -`fixationpointx (mcspx)`,
                -`fixationpointy (mcspx)`) %>%
  dplyr::arrange(., trial, fixationindex, recordingtimestamp)
```

Omit rows with is.na(count) and fixations in `x`.

```{r}
df_TR_longer_disp_only <- df_TR_longer_disp_only %>%
  dplyr::filter(., (!is.na(count))) %>%
  dplyr::filter(., category %in% c('a', 'b', 'c')) %>%
  # convert trial to integer
  dplyr::mutate(., trial = as.numeric(trial)) %>%
  dplyr::arrange(., trial, recordingtimestamp)

dim(df_TR_longer_disp_only)
```

Ok, that looks better.

```{r}
n_aois_per <- df_TR_longer_disp_only %>%
  dplyr::arrange(., trial, fixationindex, recordingtimestamp) %>%
  dplyr::group_by(., recordingtimestamp) %>%
  dplyr::summarize(., n_aois = cumsum(count))

these_aois <- (n_aois_per$n_aois == 1)

df_longer <- df_TR_longer_disp_only %>%
  dplyr::arrange(., trial, fixationindex, recordingtimestamp) 

df_merge <- df_longer %>%
  dplyr::mutate(., n_aois_per_fix = n_aois_per$n_aois) %>%
  dplyr::filter(., n_aois_per_fix == 1)
```

That seems to work, hacky or no.

Let's plot a condition to see if our scheme works.

# Plot one participant and one trial

How many trials?

```{r}
unique(df_merge$trial)
```

Looks like there are 32.

Select fixations for trial 1.

```{r}
this_trial <- df_merge %>%
  filter(., trial == 2)
```

```{r}
this_trial %>%
  ggplot(.) +
  aes(x=fixationindex, y=gazeeventduration) +
  geom_point()
```

Let's generate cumulative sums.

```{r}
this_trial_fixations <- this_trial %>%
  dplyr::filter(., count == 1) %>%
  dplyr::group_by(., category, fixationindex) %>%
  dplyr::summarize(., fix_ms = mean(gazeeventduration),
                   fix_start = min(recordingtimestamp),
                   fix_end = max(recordingtimestamp)) %>%
  dplyr::arrange(., fixationindex)

this_trial_fixations_cum_sum <- this_trial_fixations %>%
  dplyr::group_by(., category) %>%
  dplyr::summarize(., fixationindex = fixationindex,
                   cum_fix = cumsum(fix_ms), 
                   fix_start = fix_start, 
                   fix_end = fix_end) %>%
  dplyr::arrange(., fixationindex, fix_start)

start_cum_sum <- c(0, this_trial_fixations_cum_sum$cum_fix[1:length(this_trial_fixations_cum_sum)-1])

xx <- this_trial_fixations_cum_sum %>%
  tidyr::pivot_longer(., c(fix_start, fix_end), names_to = "fix_evt", values_to = "ms") %>%
  dplyr::arrange(., fixationindex, ms)

yy <- this_trial_fixations_cum_sum %>%
  dplyr::select(., fixationindex, cum_fix) %>%
  dplyr::mutate(., cum_fix_start = c(0, cum_fix[1:length(cum_fix)-1])) %>%
  tidyr::pivot_longer(., c(cum_fix_start, cum_fix), names_to = "sum_cat", values_to = "cum_sum_ms") %>%
  dplyr::arrange(., fixationindex, cum_sum_ms)

zz <- xx
zz$cum_sum_ms = yy$cum_sum_ms
```

```{r}
zz %>%
  dplyr::arrange(., category, fixationindex) %>%
  filter(., category == 'a') %>%
  ggplot(.) +
  aes(x = ms, y = cum_sum_ms, color = category) +
  geom_point() +
  geom_line()
```

```{r}
this_trial_fixations_cum_sum %>%
  ggplot(.) +
  aes(x = fix_start, y = cum_fix, color = category) +
  geom_point() +
  geom_line()
```
 
## Same participant, multiple trials
 
```{r}
# df_merge <- df_merge %>%
#   dplyr::mutate(., trial = as.numeric(trial))

these_fixations <- df_merge %>%
  dplyr::group_by(., trial, layout, target, fixationindex, category) %>%
  dplyr::summarize(., fix_ms = mean(gazeeventduration),
                   fix_start = min(recordingtimestamp)) %>%
  dplyr::arrange(., trial, fixationindex, category)

these_fixations_cum_sum <- these_fixations %>%
  dplyr::arrange(., fix_start) %>%
  dplyr::group_by(., trial, category) %>%
  dplyr::summarize(., trial = trial, layout = layout,
                   target = target,
                   fix_start = fix_start, category = category, 
                   cum_fix = cumsum(fix_ms)) %>%
  dplyr::arrange(., trial, fix_start, category)
```
 
```{r}
plot_this_trial <- function(select_trial = 1, save_it = FALSE) {
  this_trial <- dplyr::filter(these_fixations_cum_sum, trial == select_trial)
  p <- ggplot(this_trial) +
    aes(x = fix_start, y = cum_fix, color = category) +
    geom_point() +
    ggtitle(paste0("Participant TR | Trial ", this_trial$trial, ' | ',
                   this_trial$target, ' | ', this_trial$layout)) +
    geom_line()
  
  if (save_it) {
  ggsave(paste0('img/', 'TR-', this_trial$trial, '-', 
                this_trial$target, '-', this_trial$layout, '.png'),
         device = 'png')    
  }
  p
}

plot_this_trial(4)
```

