---
title: "Data Import"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: html_document
---

# Purpose

To import the Wilkinson lab data files in `.xlsx` format, and export CSVs for each participant.

# Set-up

```{r}
library(tidyverse)
```

# Import

We focus first on the files in `r (project_dir <- '~/Box/R01 Project 2 Data for Yiming&Rick/R01A-C files for transitional probabilities')`.


```{r load-csv}
csv_files <- list.files(project_dir, pattern = '\\.csv$', full.names = TRUE, )
csv_files
```

We open the second file.

```{r open-2nd}
df <- readr::read_csv(csv_files[2])
```

List the variable names.

```{r show-names}
names(df)
```

Now, list the unique participant ids.

```{r}
p_ids <- unique(df$ParticipantName)
p_ids
```

Write a helper function to filter data for each participant and export as CSV.

```{r define import-export-function}
import_by_sub_then_export <- function(this_p_id, df) {
  this_p_df <- dplyr::filter(df, ParticipantName == this_p_id)
  readr::write_csv(this_p_df, path = paste0('csv/', this_p_id, '-raw.csv'))
}
```

Test the function with the first participant in the list, e.g., `p_ids[1]`

```{r test-function}
import_by_sub_then_export(p_ids[1], df)
```

Run across list of `p_id`s.

```{r map-function-across-list}
purrr::map(p_ids, import_by_sub_then_export, df)
```

