---
title: "datacleaning"
<<<<<<< HEAD
output: html_document
=======
author: "Yiming Qian & Rick Gilmore"
date: "`r Sys.time()`"
output: github_document
>>>>>>> eb027e3fa0dc725a148a2be8691842b5d635c790
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(openxlsx)
```

<<<<<<< HEAD
list.files(path="~/")

```{r import-data}
df<-read.xlsx("data-R01A/R01_C_Data_Export_DS_newAOInames.xlsx")
```

start_with
head(df)

```{r preclean-data}
# extract the fixation 
newdata<-df[which(df$GazeEventType =='Fixation'),]
rm(df)
df<-newdata[grep(".png", newdata$MediaName), ]
rm(newdata)
newdata <- df[c(-1, -6:-17)]
rm(df)
df$condt <- as.factor(sub(".*_", "",newdata$MediaName))
rm(newdata)
# [ which(df$GazeEventType=='Fixation' ), ]
# delete the aoi condition with "all"
# df <- newdata %>% 
#   select(-contains('-ALL]')) # I shall not exclude ALL condition, it is for X. (Not right, If ABC is not 1, X is 1, it will be indicated in ALL condition )
# rm(newdata)
```

Create a new data frame with an `aoi` variable that is either NA (if there is no valid fixation among the targets) or the media name, e.g., `AOI.3B.EMO.HOT.Hit`.  (In the original, raw data file from the Tobii, there are individual columns for each AOI and condition. If the system detects a fixation within that AOI, it puts a 1 in the row for that fixation and the column for that AOI/condition.)

Here, the `3B` refers to trial 3 and `B` refers to targets that are semantically related to the actual target `A`. `C` refers to a distractor, and `X` refers to the background. `EMO` refers to the specific layout of the images. `HOT` refers to the image type. `Hit` simply means that the fixation fell within the AOI associated with this image.

```{r rearrange-data}
# extract all the aoi column into one column
df2<-df[,1:4]
df2$aoi<-""
df2$condt<-df$condt
for (i in 1:nrow(df)) {
  #for (j in 7:(ncol(newdata2)-1)) {
    # if (newdata[i,j]==1 && !is.na(newdata[i,j])) {df2$aoi[i]<-colnames(newdata)[j]}
  if (identical(which(df[i,]==1),integer(0))){
    df2$aoi[i]<-NA}
    else {
    df2$aoi[i]<-colnames(df[min(which(df[i,]==1))])}
  #}
}
# (1:nrow(mydata_2))[mydata_2[,4] == 1578]
```



Process the `aoi` variable to extract the {A, B, C, or X}. Also, I computed a duration variable.

```{r separate-data}  
df2 %>% 
  filter(!is.na(aoi))->df3
df3$category<- gsub("[^a-zA-Z]", "", substr(df3 $aoi,5,7))
table(df3$category) # check whether it is A/B/C/X
df3$category[which(df3$category=='A')] <-'A'
df3$category[which(df3$category=='B')] <-'B'
df3$category[which(df3$category=='C')] <-'C'
df3$category[which(df3$category=='X')] <-'X'
# df3$category<- as.factor(sub("[^[:alpha:]]+","",substr(df3$aoi, 5,6)))
# df3$category[df3$category=="Dis"] <-"C"   # special condition: the AOI.distractor.EMO.Hit
# df3$category[df3$category=="ar"] <- "A"    #AOI.Target.Hit
# df3$category[df3$category=="ro"]
# df3$category[df3$category=="el"]
#df3$vocab<- as.factor(substr(df3$aoi, 12,(nchar(df3$aoi)-4)))

# df3$category<-as.factor(df3$category)
# df4$category<-as.character(df4$category)
```

LP has high percentage of unclassified and saccade  
How about percentage of correct responses?
reaction time for mouse responses?

```{r create-targeted-table}
count_transition<-function(x){
  
df3$category<- as.factor(sub("[^[:alpha:]]+","",substr(df3$aoi, 6,7)))
df3$category[df3$category=="is"] <-"C"
#df3$vocab<- as.factor(substr(df3$aoi, 12,(nchar(df3$aoi)-4)))
df3 %>%
  group_by(ParticipantName,MediaName,FixationIndex,category) %>%
  summarize(duration = max(RecordingTimestamp)-min(RecordingTimestamp))   ->df4
```

Create a 4x4 transition matrix for each subject. The function `count_transition` computes this.

```{r create-targeted-table}
df4$category<-as.character(df4$category)
count_transition<-function(data){
  AA<-0
  AB<-0
  AC<-0
  AX<-0
  BA<-0
  BB<-0
  BC<-0
  BX<-0
  CA<-0
  CB<-0
  CC<-0
  CX<-0
  XA<-0
  XB<-0
  XC<-0
  XX<-0
  for (i in 1:length(x)) {
    if (identical(x[i],'A') && identical(x[i+1],'A')) {AA<-AA+1}
    else if (identical(x[i],'A') && identical(x[i+1],'B')) {AB<-AB+1}
    else if (identical(x[i],'A') && identical(x[i+1],'C')) {AC<-AC+1}
    else if (identical(x[i],'A') && identical(x[i+1],'X')) {AX<-AX+1}
    else if (identical(x[i],'B') && identical(x[i+1],'A')) {BA<-BA+1}
    else if (identical(x[i],'B') && identical(x[i+1],'B')) {BB<-BB+1}
    else if (identical(x[i],'B') && identical(x[i+1],'C')) {BC<-BC+1}
    else if (identical(x[i],'B') && identical(x[i+1],'X')) {BX<-BX+1}
    else if (identical(x[i],'C') && identical(x[i+1],'A')) {CA<-CA+1}
    else if (identical(x[i],'C') && identical(x[i+1],'B')) {CB<-CB+1}
    else if (identical(x[i],'C') && identical(x[i+1],'C')) {CC<-CC+1}
    else if (identical(x[i],'C') && identical(x[i+1],'X')) {CX<-CX+1}
    else if (identical(x[i],'X') && identical(x[i+1],'A')) {XA<-XA+1}
    else if (identical(x[i],'X') && identical(x[i+1],'B')) {XB<-XB+1}
    else if (identical(x[i],'X') && identical(x[i+1],'C')) {XC<-XC+1}
    else if (identical(x[i],'X') && identical(x[i+1],'X')) {XX<-XX+1}  } 
    return(c(AA,AB,AC,AX,BA,BB,BC,BX,CA,CB,CC,CX,XA,XB,XC,XX))
}
# step1: count in each media for each subject
df4 %>% 
  group_by(ParticipantName,MediaName) %>%
  summarise(AA=count_transition(category)[1],
         AB=count_transition(category)[2],
         AC=count_transition(category)[3],
         AX=count_transition(category)[4],

  for (i in 1:nrow(data)) {
    if ((data$category[i]=='A') && (data$category[i+1]=='A' )) {AA<-AA+1}
    else if ((data$category[i]=='A') && (data$category[i+1]=='B' )) {AB<-AB+1}
    else if ((data$category[i]=='A') && (data$category[i+1]=='C' )) {AC<-AC+1}
    else if ((data$category[i]=='A') && (data$category[i+1]=='X' )) {AX<-AX+1}
    else if ((data$category[i]=='B') && (data$category[i+1]=='A' )) {BA<-BA+1}
    else if ((data$category[i]=='B') && (data$category[i+1]=='B' )) {BB<-BB+1}
    else if ((data$category[i]=='B') && (data$category[i+1]=='C' )) {BC<-BC+1}
    else if ((data$category[i]=='B') && (data$category[i+1]=='X' )) {BX<-BX+1}
    else if ((data$category[i]=='C') && (data$category[i+1]=='A' )) {CA<-CA+1}
    else if ((data$category[i]=='C') && (data$category[i+1]=='B' )) {CB<-CB+1}
    else if ((data$category[i]=='C') && (data$category[i+1]=='C' )) {CC<-CC+1}
    else if ((data$category[i]=='C') && (data$category[i+1]=='X' )) {CX<-CX+1}
    else if ((data$category[i]=='X') && (data$category[i+1]=='A' )) {XA<-XA+1}
    else if ((data$category[i]=='X') && (data$category[i+1]=='B' )) {XB<-XB+1}
    else if ((data$category[i]=='X') && (data$category[i+1]=='C' )) {XC<-XC+1}
    else if ((data$category[i]=='X') && (data$category[i+1]=='X' )) {XX<-XX+1}  
    return(c(AA,AB,AC,AX,BA,BB,BC,BX,CA,CB,CC,CX,XA,XB,XC,XX))
  }
}
```

Now, I apply this function to each participant's data and then print out the table.

```{r}
# step1: count in each media for each subject
df4 %>% 
  group_by(ParticipantName,MediaName) %>%
  mutate(AA=count_transition(category)[1],
         AB=count_transition(category)[2],
         AC=count_transition(category)[3],
         AD=count_transition(category)[4],
>>>>>>> eb027e3fa0dc725a148a2be8691842b5d635c790
         BA=count_transition(category)[5],
         BB=count_transition(category)[6],
         BC=count_transition(category)[7],
         BX=count_transition(category)[8],
         CA=count_transition(category)[9],
         CB=count_transition(category)[10],
         CC=count_transition(category)[11],
         CX=count_transition(category)[12],
         XA=count_transition(category)[13],
         XB=count_transition(category)[14],
         XC=count_transition(category)[15],
<<<<<<< HEAD
         XX=count_transition(category)[16] ) -> df5
# step 2: count transivity for each subject
df5 %>% 
  group_by(ParticipantName) %>%
  summarise(AA=sum(AA),
         AB=sum(AB),
         AC=sum(AC),
         AX=sum(AX),
         BA=sum(BA),
         BB=sum(BB),
         BC=sum(BC),
         BX=sum(BX),
         CA=sum(CA),
         CB=sum(CB),
         CC=sum(CC),
         CX=sum(CX),
         XA=sum(XA),
         XB=sum(XB),
         XC=sum(XC),
         XX=sum(XX)) ->df6
```

```{r export-data}
write.table(df6, "data/all_soc_subjects_transitional_probability_r.txt", sep="\t", row.names = FALSE)
```

write.table(df4, "data/soc_r.txt", sep="\t", row.names = FALSE)
df4<-read.table(file = 'data/soc_r.txt', sep = '\t', fill=T, header = TRUE)

for (i in nrow(df7)) {
  if ((df4$category[i]!=df7$category[i])==TRUE) {
    print(df7[i,]}
} 
=======
         XX=count_transition(category)[16]
         )
```
>>>>>>> eb027e3fa0dc725a148a2be8691842b5d635c790
