---
title: "Plot_data"
author: "Yiming"
date: "`r Sys.time()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(MASS)
library(graphics)
library(RColorBrewer)
library(tidyr)
library(reshape2)
```

## read the file

```{r import-data}
data<-read.table(file = 'data/all_subjects_transitional_probability.txt', header = TRUE)
# rename
data$Condition<-factor( data$Condition, 
      levels = c("soc", "clock","LP","emo"), 
      labels = c("SOC", "CLOCK", "LP","EMO")) 
data$Group<-factor( data$Group, 
      levels = c("T", "U"), 
      labels = c("Control", "Down's")) 
```

## total time between 2 groups

### total time after looking at A between 2 groups

## total search between 2 groups
```{r boxplot-total}
p <- ggplot(data, aes(x=Condition, y=total/8, fill = Group)) + 
    scale_x_discrete(name = "Condition") +
    scale_y_continuous(name = "Total transition (fixation to fixation) counts") +
    geom_boxplot()+
    theme_bw() +
    theme(plot.title = element_text(size = 14, family = "Tahoma", face = "bold"),
              text = element_text(size = 12, family = "Tahoma"),
              axis.title = element_text(face="bold"),
              axis.text.x=element_text(size = 11)) 
     # + scale_fill_discrete(name="Group",
     #                    breaks=c("T", "U"),
      #                   labels=c("Control", "Down's"))
p

```
```{r lineplot-total}
df<- data %>%
  group_by(Condition, Group) %>%
  summarize(total.mean=mean(total/8),
            n=n(),
            total.se=sd(total/8)/sqrt(n))

p1<-ggplot(df, aes(x=Condition, y=total.mean, group=Group, color=Group))+
         geom_line()+
        labs(x="condition", y="Total counts")  +
        geom_pointrange(aes(ymin=total.mean-total.se, ymax=total.mean+total.se))
         # ggtitle('total translational counts') +
    #  +  scale_colour_hue(name="group",    #Legend label, use darker colors
     #                 breaks=c("T", "U"),
      #              labels=c("Control", "Down's"))+
       
p1
```
### total extra search after first-time looking at A between 2 groups

## an example of search path in one condition (?)
### Control
### Down

## 4*4 graph of average AOI counts in all subjects between 2 groups

## translation lines to each state

## Percentage of AOI from target to the other categories
### To ABCX
```{r percentage-AOI-all-after-A}
data %>%
  group_by(Group, Condition) %>%
  summarise(AA=mean(AA),
            AB=mean(AB),
            AC=mean(AC),
            AX=mean(AX)) ->df2

df2<-melt(df2, id.vars=c("Group","Condition"), variable.name="A")

p3<-ggplot(df2, aes(fill=A, y=value, x=Condition)) + 
    geom_bar( stat="identity", position="fill") +    
    facet_wrap(~Group) +
    xlab("Condition") + ylab("Percentage of AOI after looking at the targeted AOI") + # Set axis labels
   # ggtitle("Average bill for 2 people") +     # Set title
    theme_bw() 
   # + scale_colour_hue(name="AOI after looking at target AOI",    #Legend label, use darker colors
   #                   breaks=c("AA", "AB","AC","AX"),
   #                labels=c("Target AOI","Related AOI","distractors","white background"))
p3
```

### to ABC
```{r percentage-AOI-ABC-after-A}
data %>%
  group_by(Group, Condition) %>%
  summarise(AA=mean(AA),
            AB=mean(AB),
            AC=mean(AC))->df2
df2<-melt(df2, id.vars=c("Group","Condition"), variable.name="ABC")

p3<-ggplot(df2, aes(fill=ABC  , y=value, x=Condition)) + 
    geom_bar( stat="identity", position="fill") +    
    facet_wrap(~Group) +
    xlab("Condition") + ylab("Percentage of AOI after looking at the targeted AOI") + # Set axis labels
   # ggtitle("Average bill for 2 people") +     # Set title
    theme_bw()
  #  scale_colour_hue(name="AOI after looking at target AOI",    #Legend label, use darker colors
  #                    breaks=c("AA", "AB","AC","AX"),
   #                 labels=c("Target AOI","Related AOI","distractors","white background"))
p3
```