---
title: "Plot_data"
author: "Yiming"
date: "r time_sys()"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(MASS)
library(graphics)
library(RColorBrewer)
library(tidyr)
library(reshape2)
library(gplots)
```

## read the file
```{r import-data}
data<-read.table(file = 'data/all_subjects_transitional_probability.txt', header = TRUE)
# rename
data$Condition<-factor( data$Condition, 
      levels = c("soc", "clock","LP","emo"), 
      labels = c("SOC", "CLOCK", "LP","EMO")) 
data$Group<-factor( data$Group, 
      levels = c("T", "U"), 
      labels = c("TD", "DS")) 
```

## total time between 2 groups
```{r read_time_file}
t_soc<-read.table(file = 'data/SOC_SUMMARY_R.txt', sep = '\t', fill=T, header = TRUE)
```

### total time after looking at A between 2 groups

## total search between 2 groups
```{r boxplot-total}
data$Condition <- factor(data$Condition,levels = c("SOC", "LP", "EMO", "CLOCK"))
p <- ggplot(data, aes(x=Condition, y=total/8, fill = Group)) + 
    scale_x_discrete(name = "Condition") +
    scale_y_continuous(name = "Average transitional counts per trial") +
    geom_boxplot()+
    theme_bw() +
    theme(plot.title = element_text(size = 14, family = "Tahoma", face = "bold"),
              text = element_text(size = 12, family = "Tahoma"),
              axis.title = element_text(face="bold"),
              axis.text.x=element_text(size = 11)) 
     # + scale_fill_discrete(name="Group",
     #                    breaks=c("T", "U"),
      #                   labels=c("Control", "Down's"))
p

```
```{r lineplot-total}
df<- data %>%
  group_by(Condition, Group) %>%
  summarize(total.mean=mean(total/8),
            n=n(),
            total.se=sd(total/8)/sqrt(n))

p1<-ggplot(df, aes(x=Condition, y=total.mean, group=Group, color=Group))+
         geom_line()+
        labs(x="condition", y="Total counts")  +
        geom_pointrange(aes(ymin=total.mean-total.se, ymax=total.mean+total.se))
         # ggtitle('total translational counts') +
    #  +  scale_colour_hue(name="group",    #Legend label, use darker colors
     #                 breaks=c("T", "U"),
      #              labels=c("Control", "Down's"))+
       
p1
```
### total extra search after first-time looking at A between 2 groups

## an example of search path in one condition
### Control
### Down

## 4*4 graph of average AOI counts in all subjects between 2 groups
``` {r heat_map_graph}
col_breaks=c(seq(0.01,3,length=30),
   seq(3.01,6,length=30),          # for blue  # for 
seq(6.01,40,length=30))  # for red

## LP, control
matrix_LP_control<-data%>%
    filter(Condition=="LP" & Group=="Control")
matrix_LP_control.mean <- colMeans(matrix_LP_control[4:19])
data_LP_control=matrix(matrix_LP_control.mean, ncol = 4, nrow = 4,dimnames = list(From=c("Target","Related","Distractor","Background"), To=c("Target","Related","Distractor","Background")))

heatmap.2(data_LP_control,
  cellnote = data_LP_control,  # same data set for cell labels
#  main = "Average eye fixations in LP Condition of Control Group", # heat map title
  notecol="black",      # change font color of cell labels to black
  density.info="none",  # turns off density plot inside color legend
  trace="none",         # turns off trace lines inside the heat map
  margins =c(12,12),     # widens margins around plot
  col=bluered,       # use on color palette defined earlier
  # breaks=col_breaks,    # enable color transition at specified limits
  dendrogram="none",     # only draw a row dendrogram
  breaks=col_breaks,    # enable color transition at specified limits
  Colv=FALSE,Rowv=FALSE,    # no reorder
  key=F,
  srtCol=45)   # no color key

## LP, Down
matrix_LP_Down<-data%>%
    filter(Condition=="LP" & Group=="Down's")
matrix_LP_Down.mean <- colMeans(matrix_LP_Down[4:19])
data_LP_Down=matrix(matrix_LP_Down.mean, ncol = 4, nrow = 4,dimnames = list(From=c("Target","Related","Distractor","Background"), To=c("Target","Related","Distractor","Background")))

heatmap.2(data_LP_Down,
  cellnote = data_LP_Down,  # same data set for cell labels
#  main = "Average eye fixations in LP Condition of Control Group", # heat map title
  notecol="black",      # change font color of cell labels to black
  density.info="none",  # turns off density plot inside color legend
  trace="none",         # turns off trace lines inside the heat map
  margins =c(12,12),     # widens margins around plot
  col=bluered,       # use on color palette defined earlier
  # breaks=col_breaks,    # enable color transition at specified limits
  breaks=col_breaks,    # enable color transition at specified limits
  dendrogram="none",     # only draw a row dendrogram
  Colv=FALSE,Rowv=FALSE,    # no reorder
  key=F,
  srtCol=45)   

## SOC, td
matrix_SOC_td<-data%>%
    filter(Condition=="SOC" & Group=="Control")
matrix_SOC_td.mean <- colMeans(matrix_SOC_td[4:19])
data_SOC_td=matrix(matrix_SOC_td.mean, ncol = 4, nrow = 4,dimnames = list(From=c("Target","Related","Distractor","Background"), To=c("Target","Related","Distractor","Background")))

heatmap.2(data_SOC_td,
  cellnote = data_SOC_td,  # same data set for cell labels
#  main = "Average eye fixations in LP Condition of Control Group", # heat map title
  notecol="black",      # change font color of cell labels to black
  density.info="none",  # turns off density plot inside color legend
  trace="none",         # turns off trace lines inside the heat map
  margins =c(12,12),     # widens margins around plot
  col=bluered,       # use on color palette defined earlier
  breaks=col_breaks,    # enable color transition at specified limits
  dendrogram="none",     # only draw a row dendrogram
  Colv=FALSE,Rowv=FALSE,    # no reorder
  key=F,
  srtCol=45)   

## SOC, Down
matrix_SOC_Down<-data%>%
    filter(Condition=="SOC" & Group=="Down's")
matrix_SOC_Down.mean <- colMeans(matrix_SOC_Down[4:19])
data_SOC_Down=matrix(matrix_SOC_Down.mean, ncol = 4, nrow = 4,dimnames = list(From=c("Target","Related","Distractor","Background"), To=c("Target","Related","Distractor","Background")))

heatmap.2(data_SOC_Down,
  cellnote = data_SOC_Down,  # same data set for cell labels
#  main = "Average eye fixations in LP Condition of Control Group", # heat map title
  notecol="black",      # change font color of cell labels to black
  density.info="none",  # turns off density plot inside color legend
  trace="none",         # turns off trace lines inside the heat map
  margins =c(12,12),     # widens margins around plot
  col=bluered,       # use on color palette defined earlier
  breaks=col_breaks,    # enable color transition at specified limits
  dendrogram="none",     # only draw a row dendrogram
  Colv=FALSE,Rowv=FALSE,    # no reorder
  key=F,
  srtCol=45)   

## clock, td
matrix_clock_td<-data%>%
    filter(Condition=="CLOCK" & Group=="Control")
matrix_clock_td.mean <- colMeans(matrix_clock_td[4:19])
data_clock_td=matrix(matrix_clock_td.mean, ncol = 4, nrow = 4,dimnames = list(From=c("Target","Related","Distractor","Background"), To=c("Target","Related","Distractor","Background")))

heatmap.2(data_clock_td,
  cellnote = data_clock_td,  # same data set for cell labels
#  main = "Average eye fixations in LP Condition of Control Group", # heat map title
  notecol="black",      # change font color of cell labels to black
  density.info="none",  # turns off density plot inside color legend
  trace="none",         # turns off trace lines inside the heat map
  margins =c(12,12),     # widens margins around plot
  col=bluered,       # use on color palette defined earlier
  breaks=col_breaks,    # enable color transition at specified limits
  dendrogram="none",     # only draw a row dendrogram
  Colv=FALSE,Rowv=FALSE,    # no reorder
  key=F,
  srtCol=45)   

## clock, Down
matrix_clock_Down<-data%>%
    filter(Condition=="CLOCK" & Group=="Down's")
matrix_clock_Down.mean <- colMeans(matrix_clock_Down[4:19])
data_clock_Down=matrix(matrix_clock_Down.mean, ncol = 4, nrow = 4,dimnames = list(From=c("Target","Related","Distractor","Background"), To=c("Target","Related","Distractor","Background")))

heatmap.2(data_clock_Down,
  cellnote = data_clock_Down,  # same data set for cell labels
#  main = "Average eye fixations in LP Condition of Control Group", # heat map title
  notecol="black",      # change font color of cell labels to black
  density.info="none",  # turns off density plot inside color legend
  trace="none",         # turns off trace lines inside the heat map
  margins =c(12,12),     # widens margins around plot
  col=bluered,       # use on color palette defined earlier
  breaks=col_breaks,    # enable color transition at specified limits
  dendrogram="none",     # only draw a row dendrogram
  Colv=FALSE,Rowv=FALSE,    # no reorder
  key=F,
  srtCol=45)  

## emo, td
matrix_emo_td<-data%>%
    filter(Condition=="EMO" & Group=="Control")
matrix_emo_td.mean <- colMeans(matrix_emo_td[4:19])
data_emo_td=matrix(matrix_emo_td.mean, ncol = 4, nrow = 4,dimnames = list(From=c("Target","Related","Distractor","Background"), To=c("Target","Related","Distractor","Background")))

heatmap.2(data_emo_td,
  cellnote = data_emo_td,  # same data set for cell labels
#  main = "Average eye fixations in LP Condition of Control Group", # heat map title
  notecol="black",      # change font color of cell labels to black
  density.info="none",  # turns off density plot inside color legend
  trace="none",         # turns off trace lines inside the heat map
  margins =c(12,12),     # widens margins around plot
  col=bluered,       # use on color palette defined earlier
  breaks=col_breaks,    # enable color transition at specified limits
  dendrogram="none",     # only draw a row dendrogram
  Colv=FALSE,Rowv=FALSE,    # no reorder
  key=F,
  srtCol=45)   

## emo, Down
matrix_emo_Down<-data%>%
    filter(Condition=="EMO" & Group=="Down's")
matrix_emo_Down.mean <- colMeans(matrix_emo_Down[4:19])
data_emo_Down=matrix(matrix_emo_Down.mean, ncol = 4, nrow = 4,dimnames = list(From=c("Target","Related","Distractor","Background"), To=c("Target","Related","Distractor","Background")))

heatmap.2(data_emo_Down,
  cellnote = data_emo_Down,  # same data set for cell labels
#  main = "Average eye fixations in LP Condition of Control Group", # heat map title
  notecol="black",      # change font color of cell labels to black
  density.info="none",  # turns off density plot inside color legend
  trace="none",         # turns off trace lines inside the heat map
  margins =c(12,12),     # widens margins around plot
  col=bluered,       # use on color palette defined earlier
  breaks=col_breaks,    # enable color transition at specified limits
  dendrogram="none",     # only draw a row dendrogram
  Colv=FALSE,Rowv=FALSE,    # no reorder
  key=F,
  srtCol=45)   
```

## translation lines to each state

## Percentage of AOI from target to the other categories
### To ABCX
```{r percentage-AOI-all-after-A}
data %>%
  group_by(Group, Condition) %>%
  summarise(AA=mean(AA),
            AB=mean(AB),
            AC=mean(AC),
            AX=mean(AX))->df2
df2<-melt(df2, id.vars=c("Group","Condition"), variable.name="A")

p3<-ggplot(df2, aes(fill=A  , y=value, x=Condition)) + 
    geom_bar( stat="identity", position="fill") +    
    facet_wrap(~Group) +
    xlab("Condition") + ylab("Percentage of AOI after looking at the targeted AOI") + # Set axis labels
   # ggtitle("Average bill for 2 people") +     # Set title
    theme_bw() 
   # + scale_colour_hue(name="AOI after looking at target AOI",    #Legend label, use darker colors
   #                   breaks=c("AA", "AB","AC","AX"),
   #                labels=c("Target AOI","Related AOI","distractors","white background"))
p3
```

### to ABC
```{r percentage-AOI-ABC-after-A}
data %>%
  group_by(Group, Condition) %>%
  summarise(AA=mean(AA),
            AB=mean(AB),
            AC=mean(AC))->df2
df2<-melt(df2, id.vars=c("Group","Condition"), variable.name="ABC")

df2$A<- factor(df2$ABC, levels=rev(c("AA","AB","AC")), labels=rev(c("Target to Target", "Target to Related", "Target to Distractors")))
df2$Condition <- factor(df2$Condition,levels = c("SOC", "LP", "EMO", "CLOCK"))
p3<-ggplot(df2, aes(fill=A  , y=value, x=Condition)) + 
    geom_bar( stat="identity", position="fill") +   
  # scale_y_continuous(labels = scales::percent, limits=c(0,1))+
    facet_wrap(~Group) +
    xlab("Condition") +
    ylab("Percent") + 
   ggtitle("Percentage of Transitions from Target to each Stimulus Type") + # Set axis labels
    scale_fill_brewer(palette = "Blues") +
    theme_bw()+
     theme(legend.position="bottom") + 
   scale_fill_brewer(palette = "Blues") +
     guides(fill=guide_legend(title=NULL))+
    guides(fill = guide_legend(reverse = TRUE))+
      theme(plot.title = element_text(hjust = 0.5))
  #  scale_colour_hue(name="AOI after looking at target AOI",    #Legend label, use darker colors
  #                    breaks=c("AA", "AB","AC","AX"),
   #                 labels=c("Target AOI","Related AOI","distractors","white background"))
p3


```
### to ABC
```{r percentage-AOI-ABC-after-A}
data %>%
   filter(Group=="TD") %>%
  group_by(Condition) %>%
  summarise(
            AA=mean(AA),
            AB=mean(AB),
            AC=mean(AC)) ->df2_td
df2_td %>%
   group_by(Condition) %>%
   mutate(sumrow= AA + AB + AC) %>%
   mutate(A=AA/sumrow, 
          B=AB/sumrow,
          C=AC/sumrow) -> df2_td
df2_td<-df2_td[,-c(2:5)]
df2<-melt(df2_td, id.vars=c("Condition"), variable.name="ABC")

df2$A<- factor(df2$ABC, levels=c("A","B","C"), labels=c("Target to Target", "Target to Related", "Target to Distractors"))
df2$Condition <- factor(df2$Condition,levels = c("SOC", "LP", "EMO", "CLOCK"))
p7<-ggplot(data=df2, aes(x=Condition, y=value, fill=A)) +
  geom_bar(stat="identity", position=position_dodge())+
  geom_text(aes(label=as.integer(value*100)), vjust=1.6, color="black",
            position = position_dodge(0.9), size=3.5)+
  scale_fill_brewer(palette="Blues")+
   xlab("Condition") +
    ylab("Percent") + 
   ggtitle("Percentage of Transitions from Target to: (TD group)") + 
   theme_bw()+
     theme(legend.position="bottom") + 
  #  guides(fill=guide_legend(title=NULL))+
    scale_y_continuous(labels = scales::percent, limits=c(0,0.70))+
      theme(plot.title = element_text(hjust = 0.5))
   #  guides(fill = guide_legend(reverse = TRUE))
p7 
  #  scale_colour_hue(name="AOI after looking at target AOI",    #Legend label, use darker colors
  #                    breaks=c("AA", "AB","AC","AX"),
   #                 labels=c("Target AOI","Related AOI","distractors","white background"))

```

### to all
```{r AOI-ABCX-after-A}
# Calculate the cumulative sum of len for each dose
df_cumsum <- plyr::ddply(df2, "Condition",
                   transform, label_ypos=cumsum(value)- 0.5*value)
df_cumsum$A<- factor(df_cumsum$A, levels=rev(c("AA","AB","AC","AX")), labels=rev(c("Target to Target", "Target to Related", "Target to Distractors","Target to Background")))
df_cumsum$Condition <- factor(df_cumsum$Condition,levels = c("SOC", "LP", "EMO", "CLOCK"))
p4<- ggplot(data=df_cumsum, aes(x=Condition, y=value, fill=A)) +
    geom_bar(stat = "identity") +    
    facet_wrap(~Group) +
    xlab("Condition") +ylab("Frequency") +
   ggtitle("Transitions from Target to each Stimulus Type") +   # Set axis labels 
   scale_fill_brewer(palette = "Blues") +
  # geom_text(aes(y=label_ypos, label=value), vjust=2,color="black", size=3.5)+ 
  guides(fill = guide_legend(reverse = TRUE))+
  guides(fill=guide_legend(title=NULL))+
   ylim(0, 11)+ 
    theme_bw()+
  # scale_fill_discrete( labels=c("Target to Target", "Target to Related", "Target to Distractors","Target to Background")) +
  theme(legend.position="bottom") + 
   scale_fill_brewer(palette = "Blues") +
      theme(plot.title = element_text(hjust = 0.5))


p4
```

### to ABC
```{r AOI-ABC-after-A}
# Stacked barplot with multiple groups
p5<- ggplot(data=df2, aes(x=Condition, y=value, fill=ABC)) +
  geom_bar(stat="identity") +    
    facet_wrap(~Group) +
    xlab("Condition") + ylab("AOI after looking at the targeted AOI") + # Set axis labels
   # ggtitle("Average bill for 2 people") +     # Set title
    theme_bw()
p5
```

chi-square
df8<- df2 %>%
   filter(Group=="TD")
df8<- df8[,-c(1,2)]
chisq.test(df8*25)

### Mean looks to target in each trial type during the full trial. Time represents the time course of the trial, with 0 at the onset of the target noun. The proportion of looking to target was the amount of time looking at the target, divided by the amount of time looking at either image. 4 lines indicate 4 conditions in either TD group or DS group. Shading represents plus or minus one standard error of the mean
```{r get_data}
df<-read.table(file = 'data/all_soc_subjects_R.tsv', sep = '\t', fill=T, header = TRUE)
# newdata <-  filter(df,GazeEventType=="Fixation")
df2<-df[,1:3]
df<-df[,-c(4,5)]
df2$aoi<-""
for (i in 1:nrow(df)) {
  #for (j in 7:(ncol(newdata2)-1)) {
    # if (newdata[i,j]==1 && !is.na(newdata[i,j])) {df2$aoi[i]<-colnames(newdata)[j]}
  if (identical(which(df[i,]==1),integer(0))){
    df2$aoi[i]<-NA}
    else {
    df2$aoi[i]<-colnames(df[min(which(df[i,]==1))])}
  #}
}
df2$condt <- as.factor(substr(df2$MediaName, 1,5))
df2$category<- gsub("[^a-zA-Z]", "", substr(df2$aoi,5,7))
table(df2$category)
#df2$category[which(df2$category=='A')] <-'A'
#df2$category[which(df2$category=='B')] <-'B'
#df2$category[which(df2$category=='C')] <-'C'
#df2$category[which(df2$category=='X')] <-'X'
df2$Condtion<-"SOC"

add_group<-read.table(file = 'data/all_subjects_transitional_probability.txt', header = TRUE)
add_group<-add_group[,c(1,3)]
df2<-dplyr::left_join(df2, add_group, by = "ParticipantName")
df2$Group<-factor( df2$Group, 
      levels = c("T", "U"), 
      labels = c("TD", "DS")) 
df2<-df2 %>%
     group_by(ParticipantName, MediaName)  %>%
     mutate(t=row_number()*17)

df3<-df2 %>%
     group_by(ParticipantName,t, Group)  %>%
     summarize(count_A= sum(category=="A", na.rm = T),
               perc_A=count_A/8) 

# Plot theme, customizations 
y_lbl <- 'Percentage'
title_text <- ''

sd = 1
 df4 <- df3 %>%
   group_by(t, Group) %>%
   summarize(pcorr.mean=mean(perc_A),
          pcorr.sd=sd(perc_A),
          pcorr.lower_bound = pcorr.mean-sd*pcorr.sd,
          pcorr.upper_bound=pcorr.mean+sd*pcorr.sd)

#confidence band
p1 <- ggplot(df4, aes(t, pcorr.mean)) +
   geom_line(aes(color=Group), size = 2) +
   geom_ribbon(aes(ymin = pcorr.lower_bound, ymax =pcorr.upper_bound), fill = "grey70",              alpha=0.5)+       #transparency
   labs(x="time (ms)", y=y_lbl) +
   ggtitle(title_text) +
   theme_bw() 

 p1
```


### Total number of Subjects in TD group that did or did not produce at least one Target-Distracter Transition
```{r target-distractor}
df9<-data %>%
    filter(Group=="TD") %>%
    group_by(Condition) %>%
    filter(AC==0) %>%
    summarize(zero=n(), nonzero=25-n())
chisq.test(df9[,2:3])
df9<-melt(df9, id.vars=c("Condition"), variable.name="ABC")

df9$A<- factor(df9$ABC, levels=c("zero","nonzero"), labels=c("Made 0 Target-Distractor Transition", "Made 1+ Target-Distractor Transitions"))
df9$Condition <- factor(df9$Condition,levels = c("SOC", "LP", "EMO", "CLOCK"))
p10<-ggplot(df9, aes(fill=A  , y=value, x=Condition)) + 
    geom_bar( stat="identity", position=position_dodge()) + 
   geom_text(aes(label=value), vjust=1.6, color="black",
            position = position_dodge(0.9), size=3.5)+
    xlab("Condition") +
    ylab("Number of Subjects") + 
   ggtitle("Total number of Subjects in TD group \n that did or did not produce at least one Target-Distracter Transition") + # Set axis labels
    scale_fill_brewer(palette = "Paired") +
    theme_bw()+
     theme(legend.position="bottom") + 
     guides(fill=guide_legend(title=NULL))+
      theme(plot.title = element_text(hjust = 0.5))+
 #  guides(fill = guide_legend(reverse = TRUE))+
    ylim(0,25)

p10
```